\cvsection{Experience}

\cvsubsection{Bangkit Academy}{Feb 2023 -- Jan 2025}{Machine Learning Mentor \& Advisor}
\begin{itemize}
  \item Guided machine learning learners through model-building workflows, assignments, and applied project execution in a structured cohort environment.
  \item Tracked learner progress, identified technical blockers early, and delivered targeted support across core ML concepts and implementation details.
  \item Collaborated with instructors to refine learning materials and improve assignment clarity for a more execution-focused learning path.
\end{itemize}

\cvsubsection{Dibilabs by Dibimbing.id}{Mar 2023 -- Jun 2023}{SEO Intern}
\begin{itemize}
  \item Performed keyword and competitor analysis to identify content opportunities and improve search visibility across target topics.
  \item Optimized on-page content structure, metadata, and media annotations using analytics-backed SEO workflows.
  \item Monitored traffic, rankings, and keyword performance using web analytics and SEO tooling to support iterative content improvements.
\end{itemize}

\newpage
\cvsubsection{Indonesia AI}{Dec 2021 -- Oct 2022}{Mentor}
\begin{itemize}
  \item Delivered mentorship across data science, machine learning, deep learning, and computer vision topics in a structured community setting.
  \item Tracked learner progress and reported development updates to program organizers.
  \item Acted as a technical mentor and learning guide for students progressing through applied AI material.
\end{itemize}

\cvsubsection{ZettaByte Pte Ltd.}{May 2022 -- Aug 2022}{AI Developer}
\begin{itemize}
  \item Built AI application components including a student focus-level measurement system, question generation workflow, and question answering system.
  \item Deployed chatbot functionality with database integration as part of a broader AI product implementation.
  \item Monitored development execution, tracked progress, and followed through on delivery plans during implementation cycles.
\end{itemize}
