\cvsection{Selected Projects}

\textbf{Omniflow --- AI-Native Modular Enterprise Platform}\hfill {\color{SecondaryText}\small Flagship project}\par
\begin{itemize}
  \item Designed an AI-native modular enterprise platform combining intelligent workflow orchestration, LLM-powered automation, RAG pipelines, and MCP-based agentic orchestration for enterprise process automation.
  \item Built distributed infrastructure spanning Dockerized services, PostgreSQL, Redis, RabbitMQ, MinIO, and an observability stack (Prometheus, Grafana, Loki, Tempo) with telemetry-driven monitoring and cloud-native deployment on Cloudflare.
  \item Integrated systems-thinking across modular ERP modules, AI-native automation pipelines, observability tooling, and production-oriented platform architecture with end-to-end service interoperability.
  \item Explored agentic system experimentation and MCP-based orchestration patterns for enterprise workflow automation, enabling multi-step task coordination and intelligent decision routing.
\end{itemize}
\cvtech{Tech stack: Python, JavaScript, Docker, Linux, PostgreSQL, Redis, RabbitMQ, MinIO, Grafana, Loki, Tempo, LangChain, RAG, MCP, Cloudflare, PM2}

\newpage
\textbf{KTP OCR with VLM}\hfill {\color{SecondaryText}\small Selected project}\par
\begin{itemize}
  \item Built an OCR pipeline for extracting Indonesian ID card (KTP) data using a Vision Language Model, producing structured JSON output for e-KYC workflows.
  \item Engineered handling for noisy text, multi-field column layouts, and varied image quality to support downstream identity verification pipelines.
  \item Designed the extraction pipeline with inference-aware processing and structured output validation for production-oriented document intelligence.
\end{itemize}
\cvtech{Tech stack: Vision Language Model, Python, Structured Extraction, Document Intelligence, e-KYC}

\textbf{Finbot}\hfill {\color{SecondaryText}\small Selected project}\par
\begin{itemize}
  \item Developed a financial analysis web application for \^{}JKSE and S\&P 500 with real-time data retrieval, time series forecasting, and API-driven market data integration.
  \item Integrated news aggregation, YouTube insight extraction, and LLM-powered interactive Q\&A for comprehensive financial analysis and decision support.
  \item Combined forecasting models with real-time data pipelines to deliver actionable market intelligence through a unified interface.
\end{itemize}
\cvtech{Tech stack: Python, Time Series Forecasting, Financial APIs, LLM, RAG, Web Application}

\textbf{Document Translator}\hfill {\color{SecondaryText}\small Selected project}\par
\begin{itemize}
  \item Built a document translation pipeline with LLM-powered translation, supporting multi-format output downloads as PDF or TXT packaged in ZIP.
  \item Implemented document-grounded chat functionality using retrieval-based context for follow-up questions on translated content.
  \item Designed the workflow around document ingestion, chunking, translation orchestration, and output packaging for scalable document processing.
\end{itemize}
\cvtech{Tech stack: LLM, RAG, Document Processing, PDF Generation, Translation Pipeline}

\textbf{Marketplace Product Recommendation System}\hfill {\color{SecondaryText}\small Selected project}\par
\begin{itemize}
  \item Built a multi-modal recommender system for marketplace products combining keyword-based text retrieval and image similarity search.
  \item Integrated visual and textual feature extraction to improve product discovery, relevance ranking, and cross-modal recommendation accuracy.
\end{itemize}
\cvtech{Tech stack: Python, Machine Learning, Computer Vision, Recommendation Systems, Vector Retrieval}

\textbf{Palm Oil Ripeness Detection}\hfill {\color{SecondaryText}\small Selected project}\par
\begin{itemize}
  \item Developed a specialized web application for assessing palm oil fruit ripeness with real-time image analysis and ML-based classification.
  \item Delivered harvesting optimization insights and interactive tools for plantation yield tracking and operational efficiency improvement.
\end{itemize}
\cvtech{Tech stack: Machine Learning, Computer Vision, Real-Time Inference, Web Application}

\textbf{AI Interview}\hfill {\color{SecondaryText}\small Selected project}\par
\begin{itemize}
  \item Built an automated interview platform using LLM-driven language and context analysis to evaluate candidate responses.
  \item Designed the evaluation pipeline with structured prompt orchestration and context-aware scoring for consistent, AI-driven candidate assessment.
\end{itemize}
\cvtech{Tech stack: LLM, NLP, Prompt Orchestration, Web Application, Recruitment Tech}
