\cvsection{Data Infrastructure Projects}

\textbf{Omniflow Data Infrastructure}\hfill {\color{SecondaryText}\small Platform infrastructure}\par
\begin{itemize}
  \item Designed and deployed Dockerized distributed infrastructure spanning PostgreSQL, Redis, RabbitMQ, and MinIO for modular data service architecture with telemetry aggregation and operational monitoring.
  \item Built platform-oriented data infrastructure workflows spanning messaging systems, object storage, observability tooling, and distributed service interoperability.
  \item Configured data ingestion and pipeline orchestration workflows for cross-module data processing and service-to-service data flow.
\end{itemize}
\cvtech{Tech stack: Docker, PostgreSQL, Redis, RabbitMQ, MinIO, Prometheus, Grafana, Loki, Tempo}

\newpage
\textbf{Telemetry Analytics Pipeline}\hfill {\color{SecondaryText}\small Data infrastructure}\par
\begin{itemize}
  \item Built telemetry-oriented analytics workflows using ClickHouse for high-volume metrics querying, structured event processing, and operational telemetry analysis.
  \item Integrated Grafana dashboards and observability pipelines for real-time infrastructure visibility, metrics collection, and telemetry-driven diagnostics.
  \item Explored time-series querying and infrastructure analytics workflows across distributed containerized environments.
\end{itemize}
\cvtech{Tech stack: ClickHouse, Grafana, Telemetry, SQL, Docker, Prometheus}

\textbf{RAG Retrieval Pipeline}\hfill {\color{SecondaryText}\small Data pipeline}\par
\begin{itemize}
  \item Designed retrieval-oriented ingestion and indexing workflows for structured multi-document information access using vector-based retrieval approaches.
  \item Built orchestration-aware retrieval pipeline supporting document chunking, context-aware ranking, and grounded response generation.
  \item Integrated structured extraction and ingestion workflows for scalable document processing and retrieval orchestration.
\end{itemize}
\cvtech{Tech stack: Python, RAG, LangChain, Vector Retrieval, Document Processing, Ingestion}

\textbf{Financial Forecasting Pipeline}\hfill {\color{SecondaryText}\small Data pipeline}\par
\begin{itemize}
  \item Developed a real-time data ingestion pipeline for stock market analysis with API-driven time-series workflows and structured processing.
  \item Integrated time-series forecasting models with live data feeds for continuous prediction and market intelligence delivery.
  \item Built ETL-aware ingestion and transformation workflows for structured financial data processing and analytics.
\end{itemize}
\cvtech{Tech stack: Python, Time-Series Processing, Financial APIs, Data Ingestion, ETL, Forecasting}

\textbf{Document Intelligence Pipeline}\hfill {\color{SecondaryText}\small Data pipeline}\par
\begin{itemize}
  \item Built a document processing pipeline with OCR-based structured extraction, chunking, and translation orchestration for multi-format document workflows.
  \item Implemented retrieval-aware processing with grounded follow-up querying for document-grounded intelligence extraction.
\end{itemize}
\cvtech{Tech stack: Python, OCR, Structured Extraction, Document Processing, RAG}

\textbf{Monitoring \& Observability Pipeline}\hfill {\color{SecondaryText}\small Monitoring infrastructure}\par
\begin{itemize}
  \item Deployed a full observability pipeline using Prometheus for metrics collection, Loki for log aggregation, and Tempo for distributed tracing.
  \item Configured Grafana dashboards for real-time infrastructure monitoring, alerting, and operational telemetry visualization.
  \item Built telemetry-driven monitoring workflows for infrastructure visibility and operational diagnostics across distributed services.
\end{itemize}
\cvtech{Tech stack: Prometheus, Grafana, Loki, Tempo, Telemetry, Monitoring, Alerting}
