\cvsection{Platform \& Infrastructure Projects}

\textbf{Omniflow Platform Infrastructure}\hfill {\color{SecondaryText}\small Platform infrastructure}\par
\begin{itemize}
  \item Designed and deployed Dockerized distributed infrastructure spanning PostgreSQL, Redis, RabbitMQ, and MinIO for modular platform service architecture.
  \item Built observability-oriented monitoring stack with Prometheus, Grafana, Loki, and Tempo integrated into the platform for telemetry, operational visibility, and infrastructure diagnostics.
  \item Configured Cloudflare Tunnel for secure external access and PM2 for process orchestration across containerized services.
  \item Built CI/CD-oriented deployment workflows using Docker, GitHub Actions, and containerized service environments for infrastructure automation.
\end{itemize}
\cvtech{Tech stack: Docker, PostgreSQL, Redis, RabbitMQ, MinIO, Prometheus, Grafana, Loki, Tempo, Cloudflare, PM2, GitHub Actions}

\newpage
\textbf{Monitoring \& Observability Stack}\hfill {\color{SecondaryText}\small Monitoring infrastructure}\par
\begin{itemize}
  \item Deployed full observability pipeline using Prometheus for metrics collection, Loki for log aggregation, Tempo for distributed tracing, and Grafana for dashboarding and alerting.
  \item Integrated Zabbix and LibreNMS for SNMP-based infrastructure health monitoring, operational diagnostics, and multi-protocol telemetry aggregation.
  \item Implemented OpenTelemetry instrumentation for unified telemetry collection across services and platform infrastructure components.
\end{itemize}
\cvtech{Tech stack: Prometheus, Grafana, Loki, Tempo, Zabbix, LibreNMS, OpenTelemetry, SNMP, Alerting}

\textbf{Hybrid Homelab Infrastructure}\hfill {\color{SecondaryText}\small Homelab}\par
\begin{itemize}
  \item Built a hybrid homelab environment using Proxmox virtualization, Docker containerization, and Linux-based services for infrastructure experimentation and operational skill development.
  \item Configured VPN tunnels with WireGuard and Tailscale for secure remote access across distributed nodes and hybrid cloud connectivity.
  \item Integrated VPS deployment with local infrastructure for hybrid cloud workflows spanning compute, storage, and networking.
  \item Deployed monitoring stack (Prometheus, Grafana, Zabbix) for operational visibility across distributed infrastructure.
\end{itemize}
\cvtech{Tech stack: Proxmox, Docker, Linux, WireGuard, Tailscale, VPS, Prometheus, Grafana, Zabbix}

\textbf{Cloudflare Tunnel \& Remote Infrastructure Access}\hfill {\color{SecondaryText}\small Network architecture}\par
\begin{itemize}
  \item Deployed Cloudflare Tunnel for secure external exposure of internal services without open inbound ports.
  \item Combined with WireGuard and Tailscale for layered remote access architecture supporting hybrid work and multi-site connectivity.
\end{itemize}
\cvtech{Tech stack: Cloudflare Tunnel, WireGuard, Tailscale, VPN, Remote Access}
