\cvsection{Infrastructure Projects}

\textbf{Hybrid Homelab Infrastructure}\hfill {\color{SecondaryText}\small Homelab}\par
\begin{itemize}
  \item Built a hybrid homelab environment using Proxmox virtualization, Docker containerization, and Linux-based services for infrastructure experimentation, deployment practice, and operational skill development.
  \item Configured VPN tunnels with WireGuard and Tailscale for secure remote access across distributed nodes and hybrid cloud connectivity.
  \item Deployed monitoring stack (Prometheus, Grafana, Loki, Tempo, Zabbix) for centralized monitoring, log aggregation, telemetry-driven infrastructure visibility, and incident diagnostics.
\end{itemize}
\cvtech{Tech stack: Proxmox, Docker, Linux, WireGuard, Tailscale, Prometheus, Grafana, Loki, Tempo, Zabbix}

\newpage
\textbf{Multi-WAN MikroTik Infrastructure}\hfill {\color{SecondaryText}\small Network deployment}\par
\begin{itemize}
  \item Configured MikroTik-based multi-WAN setup with failover, policy-based routing, and VLAN segmentation for network isolation and traffic management.
  \item Implemented NAT rules, firewall policies, DHCP servers, and DNS forwarding for structured internal network operations and service continuity.
  \item Troubleshot WAN failover behavior, routing loops, and VLAN misconfigurations across production and lab environments.
\end{itemize}
\cvtech{Tech stack: MikroTik, RouterOS, Multi-WAN, VLAN, NAT, Firewall, DHCP, DNS}

\textbf{Omniflow Infrastructure Stack}\hfill {\color{SecondaryText}\small Platform infrastructure}\par
\begin{itemize}
  \item Designed and deployed Dockerized distributed infrastructure spanning PostgreSQL, Redis, RabbitMQ, and MinIO for modular service architecture.
  \item Built monitoring and observability pipeline with Prometheus, Grafana, Loki, Tempo, and LibreNMS for telemetry, operational visibility, and SNMP-based network monitoring.
  \item Configured Cloudflare Tunnel for secure external access and PM2 for process orchestration across containerized services.
\end{itemize}
\cvtech{Tech stack: Docker, PostgreSQL, Redis, RabbitMQ, MinIO, Prometheus, Grafana, LibreNMS, Cloudflare, PM2}

\textbf{Monitoring \& Observability Stack}\hfill {\color{SecondaryText}\small Monitoring infrastructure}\par
\begin{itemize}
  \item Deployed monitoring infrastructure using Prometheus for metrics collection, Loki for log aggregation, Tempo for distributed tracing, and Grafana for dashboarding and alerting.
  \item Integrated Zabbix and LibreNMS for SNMP-based infrastructure health monitoring, network device visibility, and operational alerting workflows.
  \item Configured Grafana dashboards for real-time infrastructure monitoring, alerting, and operational telemetry visualization.
\end{itemize}
\cvtech{Tech stack: Prometheus, Grafana, Loki, Tempo, Zabbix, LibreNMS, SNMP, Telemetry, Alerting}

\textbf{IP Surveillance \& Remote Monitoring Deployment}\hfill {\color{SecondaryText}\small Field infrastructure}\par
\begin{itemize}
  \item Configured IP camera and NVR environments with segmented VLAN architecture and remote access integration for surveillance infrastructure.
  \item Combined VPN and Cloudflare Tunnel connectivity for secure remote monitoring and infrastructure access.
\end{itemize}
\cvtech{Tech stack: IP Camera, NVR, PoE, MikroTik, VLAN, VPN, Cloudflare Tunnel}

\textbf{Cloudflare Tunnel \& Remote Infrastructure Access}\hfill {\color{SecondaryText}\small Network architecture}\par
\begin{itemize}
  \item Deployed Cloudflare Tunnel for secure external exposure of internal services without open inbound ports.
  \item Combined with WireGuard and Tailscale for layered remote access architecture supporting hybrid work and multi-site connectivity.
\end{itemize}
\cvtech{Tech stack: Cloudflare Tunnel, WireGuard, Tailscale, VPN, Remote Access}

\textbf{MikroTik + Ruijie Network Design}\hfill {\color{SecondaryText}\small Campus network}\par
\begin{itemize}
  \item Designed and configured campus-style network using MikroTik routing and Ruijie switching with VLAN segmentation and inter-VLAN routing.
  \item Implemented access control policies, spanning tree protocol, and trunk/link aggregation for resilient network topology.
\end{itemize}
\cvtech{Tech stack: MikroTik, Ruijie, VLAN, Inter-VLAN Routing, STP, Link Aggregation}
